Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-17 material/expstimuli/audio/tweaked/analysis.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Histogram
```{r ioi-distribution, echo = FALSE}
gghistogram(dt_ioi[SubArt != "NA"], x = "IOI", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# KOT
- For art_only and high stimuli, there should be a bimodal distribution to represent legato and staccato.

- For dyn_only and low stimuli, there should be a normal distribution.

```{r kot, include = FALSE}
data_onset$KOT <- NA
for (row in 1:nrow(data_onset)){
   if (row < nrow(data_onset)){
      data_onset$KOT[row+1] <- data_offset$time[row] - data_onset$time[row+1] # offset(n) - onset(n+1)
   }
}

@@

## Histogram
```{r kot-distribution, echo = FALSE}
gghistogram(dt_kot[SubArt != "NA"], x = "KOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

## Tweak
- For dyn_only and low stimuli, it seems the KOT values are too close to the staccato range. We calculated the difference between the mean of each stimulus and the grand mean of art_only and high stimuli and add that difference to all KOT values for dyn_only and low, so that the KOT values should shift closer to the grand mean of art_only and high stimuli.

```{r kot-tweak, echo = FALSE}
# grandMean of art_only & high stimuli
kot_grandMean <- mean(dt_kot[grepl("art_only", MidFile) | grepl("high", MidFile) & SubArt != "NA"]$KOT)

# calculate the diff between each KOT mean and grandMean
tweak_data <- dt_kot[grepl("dyn_only", MidFile) | grepl("low", MidFile) & SubArt != "NA", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
tweak_data$Diff <- abs(tweak_data$Mean-kot_grandMean)
tweak_data

@@

## Histogram (Fixed KOT)
```{r kot-distribution-fixed, echo = FALSE}
gghistogram(dt_kot[SubArt != "NA"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# KV

```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$NoteOnsetNr <- rep(1:72, nrow(dt_vel)/72)
# assign Subcomponents
# for each note
# Legato
for (phrase in 1:length(ls_legato_2)){
   for (note in 1:length(ls_legato_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_legato_2[[phrase]][note]]$SubArt <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato_2)){
   for (note in 1:length(ls_staccato_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_staccato_2[[phrase]][note]]$SubArt <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte_2)){
   for (note in 1:length(ls_forte_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_forte_2[[phrase]][note]]$SubDyn <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano_2)){
   for (note in 1:length(ls_piano_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_piano_2[[phrase]][note]]$SubDyn <- "Piano"
   }
}
```

## Histogram
```{r vel-distribution, echo = FALSE}
gghistogram(dt_vel[SubArt != "NA"], x = "Velocity", facet.by = "MidFile", color = "SubDyn", bins = 50, rug = TRUE)
```

@@

## Histogram
```{r vel-diff-distribution, echo = FALSE}
gghistogram(dt_vel_diff[SubDyn == "FtoP" | SubDyn == "PtoF"], x = "Diff", facet.by = "MidFile", color = "SubDyn", bins = 50, rug = TRUE)
```

@@

# Export stimuli with fixed KOT as mid files
```{r export, include = FALSE}
# fix time for onset and offset data
data_offset$timeFixed <- data_onset$time
data_offset$timeFixed <- data_offset$time
for (midfile in unique(tweak_data$MidFile)){
   # offset[i] = onset[i+1]+KOT[i]
   for (i in 1:nrow(data_onset[MidFile == midfile])-1){
      data_offset[MidFile == midfile][i]$timeFixed <- data_onset[MidFile == midfile][i+1]$time+dt_kot[MidFile == midfile][i]$FixedKOT
   }
}

for (stim in unique(data_onset$MidFile)){
   onset <- data_onset[MidFile == stim]
   offset <- data_offset[MidFile == stim]
   instance <- rbind(onset, offset)
   # round timeFixed
   instance$timeFixed <- round(instance$timeFixed, 0)
   # Note_On/Off >> 1 or 0
   instance$KeyOnOff <- 0
   instance[event == "Note On"]$KeyOnOff <- 1
   # sort by timeFixed
   instance <- instance[order(timeFixed)]

   filename = paste(stim, ".txt", sep = "")
   fwrite(instance, filename)
}
```

```{bash, echo = TRUE}
# python
source /Users/atsukotominaga/Pyenv/bin/activate
python mid_export.py
```

>>>>

## Histogram
```{r ioi-distribution, echo = FALSE}
# change labelling
dt_ioi[MidFile == "high_1"]$MidFile <- "both_1"
dt_ioi[MidFile == "high_2"]$MidFile <- "both_2"
dt_ioi[MidFile == "high_3"]$MidFile <- "both_3"
dt_ioi[MidFile == "high_4"]$MidFile <- "both_4"
dt_ioi[MidFile == "low_1"]$MidFile <- "none_1"
dt_ioi[MidFile == "low_2"]$MidFile <- "none_2"
dt_ioi[MidFile == "low_3"]$MidFile <- "none_3"
dt_ioi[MidFile == "low_4"]$MidFile <- "none_4"

gghistogram(dt_ioi[SubArt != "NA"], x = "IOI", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# KOT
```{r kot, include = FALSE}
data_onset$KOT <- NA
for (row in 1:nrow(data_onset)){
   if (row < nrow(data_onset)){
      data_onset$KOT[row+1] <- data_offset$time[row] - data_onset$time[row+1] # offset(n) - onset(n+1)
   }
}

@@

## Histogram

- For art_only and both stimuli, there should be a bimodal distribution to represent the implementation of legato and staccato.

- For dyn_only and none stimuli, there should be a normal distribution.

```{r kot-distribution, echo = FALSE}
# change labelling
dt_kot[MidFile == "high_1"]$MidFile <- "both_1"
dt_kot[MidFile == "high_2"]$MidFile <- "both_2"
dt_kot[MidFile == "high_3"]$MidFile <- "both_3"
dt_kot[MidFile == "high_4"]$MidFile <- "both_4"
dt_kot[MidFile == "low_1"]$MidFile <- "none_1"
dt_kot[MidFile == "low_2"]$MidFile <- "none_2"
dt_kot[MidFile == "low_3"]$MidFile <- "none_3"
dt_kot[MidFile == "low_4"]$MidFile <- "none_4"

gghistogram(dt_kot[SubArt != "NA" & SubArt != "LtoS" & SubArt != "StoL"], x = "KOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

## Tweak
- For dyn_only and none stimuli, it seems the KOT values are too close to the staccato range. We calculated the difference between the mean of each stimulus and the grand mean of art_only and both stimuli and add that difference to all KOT values for dyn_only and none stimuli, so that the KOT values should shift closer to the grand mean of art_only and both stimuli.

## Histogram (Fixed KOT)
```{r kot-tweak, echo = FALSE}
# grandMean of art_only & both stimuli
kot_grandMean <- mean(dt_kot[grepl("art_only", MidFile) | grepl("both", MidFile) & SubArt != "NA"]$KOT)

# calculate the diff between each KOT mean and grandMean
tweak_data <- dt_kot[grepl("dyn_only", MidFile) | grepl("none", MidFile) & SubArt != "NA", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
tweak_data$Diff <- round(abs(tweak_data$Mean-kot_grandMean), 0)
tweak_data

@@

```{r kot-distribution-fixed, echo = FALSE}
gghistogram(dt_kot[SubArt != "NA" & SubArt != "LtoS" & SubArt != "StoL"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# KV
```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$NoteOnsetNr <- rep(1:72, nrow(dt_vel)/72)
# assign Subcomponents
# for each note
# Legato
for (phrase in 1:length(ls_legato_2)){
   for (note in 1:length(ls_legato_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_legato_2[[phrase]][note]]$SubArt <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato_2)){
   for (note in 1:length(ls_staccato_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_staccato_2[[phrase]][note]]$SubArt <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte_2)){
   for (note in 1:length(ls_forte_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_forte_2[[phrase]][note]]$SubDyn <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano_2)){
   for (note in 1:length(ls_piano_2[[phrase]])){
     dt_vel[NoteOnsetNr == ls_piano_2[[phrase]][note]]$SubDyn <- "Piano"
   }
}
```

## Histogram

- For dyn_only and both stimuli, there should be a bimodal distribution to represent the implementation of forte and piano.

- For art_only and none stimuli, there should be a normal distribution.

```{r vel-distribution, echo = FALSE}
# change labelling
dt_vel[MidFile == "high_1"]$MidFile <- "both_1"
dt_vel[MidFile == "high_2"]$MidFile <- "both_2"
dt_vel[MidFile == "high_3"]$MidFile <- "both_3"
dt_vel[MidFile == "high_4"]$MidFile <- "both_4"
dt_vel[MidFile == "low_1"]$MidFile <- "none_1"
dt_vel[MidFile == "low_2"]$MidFile <- "none_2"
dt_vel[MidFile == "low_3"]$MidFile <- "none_3"
dt_vel[MidFile == "low_4"]$MidFile <- "none_4"

gghistogram(dt_vel[SubArt != "NA"], x = "Velocity", facet.by = "MidFile", color = "SubDyn", bins = 50, rug = TRUE)
```

@@

## Histogram

- For dyn_only and both stimuli, there should be a bimodal distribution to represent the transition from forte to piano or from piano to forte.

- For art_only and none stimuli, there should be a normal distribution.

```{r vel-diff-distribution, echo = FALSE}
# change labelling
dt_vel_diff[MidFile == "high_1"]$MidFile <- "both_1"
dt_vel_diff[MidFile == "high_2"]$MidFile <- "both_2"
dt_vel_diff[MidFile == "high_3"]$MidFile <- "both_3"
dt_vel_diff[MidFile == "high_4"]$MidFile <- "both_4"
dt_vel_diff[MidFile == "low_1"]$MidFile <- "none_1"
dt_vel_diff[MidFile == "low_2"]$MidFile <- "none_2"
dt_vel_diff[MidFile == "low_3"]$MidFile <- "none_3"
dt_vel_diff[MidFile == "low_4"]$MidFile <- "none_4"

gghistogram(dt_vel_diff[SubDyn == "FtoP" | SubDyn == "PtoF"], x = "Diff", facet.by = "MidFile", color = "SubDyn", bins = 50, rug = TRUE)
```

@@

```{r export, include = FALSE}
knitr::purl("analysis.Rmd")
```

<!-- # Export stimuli with fixed KOT as mid files -->
<!-- ```{r export, include = FALSE} -->
<!-- # remove unnecessary columns -->
<!-- data_onset$IOI <- NULL -->
<!-- data_onset$KOT <- NULL -->
<!-- data_onset$Diff <- NULL -->
<!-- # fix time for onset and offset data -->
<!-- data_onset$timeFixed <- data_onset$time -->
<!-- data_offset$timeFixed <- data_offset$time -->
<!-- for (midfile in unique(tweak_data$MidFile)){ -->
<!--    # offset[i] = onset[i+1]+KOT[i] -->
<!--    for (i in 1:nrow(data_onset[MidFile == midfile])-1){ -->
<!--       data_offset[MidFile == midfile][i]$timeFixed <- data_onset[MidFile == midfile][i+1]$time+dt_kot[MidFile == midfile][i]$FixedKOT -->
<!--    } -->
<!-- } -->

<!-- # export each instance as txt file -->
<!-- for (stim in unique(data_onset$MidFile)){ -->
<!--    onset <- data_onset[MidFile == stim] -->
<!--    offset <- data_offset[MidFile == stim] -->
<!--    instance <- rbind(onset, offset) -->
<!--    # Note_On/Off >> 1 or 0 -->
<!--    instance$KeyOnOff <- 0 -->
<!--    instance[event == "Note On"]$KeyOnOff <- 1 -->
<!--    # sort by timeFixed -->
<!--    instance <- instance[order(timeFixed)] -->

<!--    filename = paste(stim, ".txt", sep = "") -->
<!--    fwrite(instance, filename) -->
<!-- } -->
<!-- ``` -->

<!-- ```{bash, echo = TRUE} -->
<!-- # python -->
<!-- source /Users/atsukotominaga/Pyenv/bin/activate -->
<!-- python mid_export.py -->
<!-- ``` -->

### 2023-01-17 paper/manuscript.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r plot-kot-1, out.width = "100%", fig.cap = "\\label{fig:kot-1}KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_kot_1 <- image_append(c(img_leg_all_plot, img_sta_all_plot))
img_kot_1 <- image_scale(img_kot_1, "2200")
image_write(img_kot_1, path = here("paper/image", "Fig3.tiff"), format = "tiff")
img_kot_1
```

```{r plot-vel-1, out.width = "100%", fig.cap = "\\label{fig:vel-1}KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_1 <- image_append(c(img_for_all_plot, img_pia_all_plot))
img_vel_1 <- image_scale(img_vel_1, "2200")
image_write(img_vel_1, path = here("paper/image", "Fig4.tiff"), format = "tiff")
img_vel_1
```

```{r plot-vel-diff-1, out.width = "100%", fig.cap = "\\label{fig:vel-diff-1}KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_diff_1 <- image_append(c(img_ftop_all_plot, img_ptof_all_plot))
img_vel_diff_1 <- image_scale(img_vel_diff_1, "2200")
image_write(img_vel_diff_1, path = here("paper/image", "Fig5.tiff"), format = "tiff")
img_vel_diff_1
```

```{r plot-ioi-1, out.width = "100%", fig.cap = "\\label{fig:ioi-1}IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_1 <- image_scale(img_ioi_all_plot, "2200")
image_write(img_ioi_1, path = here("paper/image", "Fig2.tiff"), format = "tiff")
img_ioi_1
```

@@

```{r supplementary, out.width = "100%", fig.cap = "\\label{fig:supplementary}Schematic representation of stimuli generation processes", echo = FALSE}
here::i_am("README.md")
stim <- image_border(image_read(here("paper/image", "supplementary.png")), "#FFFFFF", "140x140")
image_write(stim, path = here("paper/image", "Fig10.tiff"), format = "tiff")
stim
```

@@

kot_profiles <- gghistogram(dt_kot[SubArt != "NA"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)

@@

```{r plot-s-ioi, out.width = "100%", fig.cap = "\\label{fig:s-ioi}A"}
img_s_ioi_profiles
```

```{r plot-s-kot, out.width = "100%", fig.cap = "\\label{fig:s-kot}A"}
img_s_kot_profiles
```

```{r plot-s-vel, out.width = "100%", fig.cap = "\\label{fig:s-vel}A"}
img_s_vel_profiles
```

```{r plot-s-vel-diff, out.width = "100%", fig.cap = "\\label{fig:s-vel-diff}A"}
img_s_vel_diff_profiles
```

@@

```{r plot-kot-2, out.width = "100%", fig.cap = "\\label{fig:kot-2}Comparison with the baseline performance in terms of KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_kot_2 <- image_append(c(img_leg_ca_plot, img_sta_ca_plot))
img_kot_2 <- image_scale(img_kot_2, "2200")
image_write(img_kot_2, path = here("paper/image", "Fig7.tiff"), format = "tiff")
img_kot_2
```

```{r plot-vel-2, out.width = "100%", fig.cap = "\\label{fig:vel-2}Comparison with the baseline performance in terms of KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_2 <- image_append(c(img_for_ca_plot, img_pia_ca_plot))
img_vel_2 <- image_scale(img_vel_2, "2200")
image_write(img_vel_2, path = here("paper/image", "Fig8.tiff"), format = "tiff")
img_vel_2
```

```{r plot-vel-diff-2, out.width = "100%", fig.cap = "\\label{fig:vel-diff-2}Comparison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_diff_2 <- image_append(c(img_ftop_ca_plot, img_ptof_ca_plot))
img_vel_diff_2 <- image_scale(img_vel_diff_2, "2200")
image_write(img_vel_diff_2, path = here("paper/image", "Fig9.tiff"), format = "tiff")
img_vel_diff_2
```

```{r plot-ioi-2, out.width = "100%", fig.cap = "\\label{fig:ioi-2}Comparison with the baseline performance in terms of IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_2 <- image_scale(img_ioi_ca_plot, "2200")
image_write(img_ioi_2, path = here("paper/image", "Fig6.tiff"), format = "tiff")
img_ioi_2
```

>>>>

```{r plot-kot-1, out.width = "100%", fig.cap = "\\label{fig:kot-1}KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_kot_1 <- image_append(c(img_leg_all_plot, img_sta_all_plot))
img_kot_1 <- image_scale(img_kot_1, "2200")
image_write(img_kot_1, path = here("paper/image", "Fig2.tiff"), format = "tiff")
img_kot_1
```

```{r plot-vel-1, out.width = "100%", fig.cap = "\\label{fig:vel-1}KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_1 <- image_append(c(img_for_all_plot, img_pia_all_plot))
img_vel_1 <- image_scale(img_vel_1, "2200")
image_write(img_vel_1, path = here("paper/image", "Fig3.tiff"), format = "tiff")
img_vel_1
```

```{r plot-vel-diff-1, out.width = "100%", fig.cap = "\\label{fig:vel-diff-1}KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_diff_1 <- image_append(c(img_ftop_all_plot, img_ptof_all_plot))
img_vel_diff_1 <- image_scale(img_vel_diff_1, "2200")
image_write(img_vel_diff_1, path = here("paper/image", "Fig4.tiff"), format = "tiff")
img_vel_diff_1
```

```{r plot-ioi-1, out.width = "100%", fig.cap = "\\label{fig:ioi-1}IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_1 <- image_scale(img_ioi_all_plot, "2200")
image_write(img_ioi_1, path = here("paper/image", "Fig5.tiff"), format = "tiff")
img_ioi_1
```

@@

```{r supplementary, out.width = "100%", fig.cap = "\\label{fig:supplementary}Schematic representation of the stimuli generation process.", echo = FALSE}
here::i_am("README.md")
supplementary <- image_border(image_read(here("paper/image", "supplementary.png")), "#FFFFFF", "140x140")
image_write(supplementary, path = here("paper/image", "Fig6.tiff"), format = "tiff")
supplementary
```

@@

kot_profiles <- gghistogram(dt_kot[SubArt != "NA" & SubArt != "LtoS" & SubArt != "StoL"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)

@@

```{r plot-s-ioi, out.width = "100%", fig.cap = "\\label{fig:s-ioi}Histogram of interonset intervals (IOIs) for each recording. Since we fixed the tempo performance feature across 4 instances, IOI profiles were identical for each type."}
image_write(img_s_ioi_profiles, path = here("paper/image", "Fig7.tiff"), format = "tiff")
img_s_ioi_profiles
```

```{r plot-s-kot, out.width = "100%", fig.cap = "\\label{fig:s-kot}Histogram of Key-overlap time (KOT) for each recording. For art-only and both recordings, there is a bimodal distribution to represent the implementation of legato and staccato. For dyn-only and none recordings, there is no bimodal distribution (no difference between legato and staccato parts of performance). Red bars indicate KOT values where legato is notated. Blue bars indicate KOT values where staccato is notated."}
image_write(img_s_kot_profiles, path = here("paper/image", "Fig8.tiff"), format = "tiff")
img_s_kot_profiles
```

```{r plot-s-vel, out.width = "100%", fig.cap = "\\label{fig:s-vel}Histogram of key velocity (KV) for each recording. For dyn-only and both recordings, there is a bimodal distribution to represent the implementation of forte and piano. For art-only and none recordings, there is no bimodal distribution (no difference between forte and piano parts of performance). Red bars indicate KV values where forte is notated. Blue bars indicate KV values where piano is notated."}
image_write(img_s_vel_profiles, path = here("paper/image", "Fig9.tiff"), format = "tiff")
img_s_vel_profiles
```

```{r plot-s-vel-diff, out.width = "100%", fig.cap = "\\label{fig:s-vel-diff}Histogram of KV difference for each recording. For dyn-only and both recordings, there is a bimodal distribution to represent the transition from forte to piano or from piano to forte. For art-only and none recordings, there is no bimodal distribution (no contrast difference in transition parts between forte and piano). Red bars indicate KV difference of the transition from forte to piano. Blue bars indicate KV difference of the transition from piano to forte."}
image_write(img_s_vel_diff_profiles, path = here("paper/image", "Fig10.tiff"), format = "tiff")
img_s_vel_diff_profiles
```

@@

```{r plot-kot-2, out.width = "100%", fig.cap = "\\label{fig:kot-2}Comparison with the baseline performance in terms of KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_kot_2 <- image_append(c(img_leg_ca_plot, img_sta_ca_plot))
img_kot_2 <- image_scale(img_kot_2, "2200")
image_write(img_kot_2, path = here("paper/image", "Fig11.tiff"), format = "tiff")
img_kot_2
```

```{r plot-vel-2, out.width = "100%", fig.cap = "\\label{fig:vel-2}Comparison with the baseline performance in terms of KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_2 <- image_append(c(img_for_ca_plot, img_pia_ca_plot))
img_vel_2 <- image_scale(img_vel_2, "2200")
image_write(img_vel_2, path = here("paper/image", "Fig12.tiff"), format = "tiff")
img_vel_2
```

```{r plot-vel-diff-2, out.width = "100%", fig.cap = "\\label{fig:vel-diff-2}Comparison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
# combine
img_vel_diff_2 <- image_append(c(img_ftop_ca_plot, img_ptof_ca_plot))
img_vel_diff_2 <- image_scale(img_vel_diff_2, "2200")
image_write(img_vel_diff_2, path = here("paper/image", "Fig13.tiff"), format = "tiff")
img_vel_diff_2
```

```{r plot-ioi-2, out.width = "100%", fig.cap = "\\label{fig:ioi-2}Comparison with the baseline performance in terms of IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_2 <- image_scale(img_ioi_ca_plot, "2200")
image_write(img_ioi_2, path = here("paper/image", "Fig14.tiff"), format = "tiff")
img_ioi_2
```
